Exploring Local Explanations of Nonlinear Models Using Animated Linear Projections

### 2023-05-21 jss/cheem_paper.tex
added paragraph on available R packages

Explainable Artificial Intelligence (XAI) is an emerging field of
research focused on methods for the interpreting of models
\citep{adadi_peeking_2018, arrieta_explainable_2020}. A class of
techniques called \emph{local explanations}, provide methods to
approximate linear variable importance at the location of each
observation or the predictions at a specific point in the data domain.
Because these are point-specific, it is challenging to comprehensively
visualize them to understand a model. There are common approaches for
visualizing high-dimensional data as a whole, but what is needed are new
approaches for viewing these individual local explanations, in relation
to the whole.

For multivariate data visualization, a \emph{tour}
\citep{asimov_grand_1985, buja_grand_1986, lee_state_2021} of linear
data projections onto a lower-dimensional space, could be an element of
XAI, complementing local explanations. Applying tours to model
interpretation is recommended in \citet{wickham_visualizing_2015}
primarily to examine the fitted model in the space of the data.
\citet{cook_interactive_2007} describe the use of tours for exploring
classification boundaries and model diagnostics
\citep{Caragea2008, lee_pptree_2013, da_silva_projection_2021}. There
are various types of tours. In a \emph{manual} or radial tour
\citep{cook_manual_1997, spyrison_spinifex_2020}, the path of linear
projections is defined by changing the contribution of a selected
variable. We propose to use this to scrutinize a local explanation. This
approach could be considered to be a counter-factual, what-if analysis,
such as \emph{ceteris paribus} (``other things held constant'') profiles
\citep{biecek_ceterisparibus_2020}.

The remainder of this paper is organized as follows. Section
\ref{sec:explanations} covers the background of the local explanation
and the traditional visuals produced. Section \ref{sec:tour} explains
the tours and particularly the radial manual tour. Section
\ref{sec:cheemviewer} discusses the visual layout in the graphical user
interface and how it facilitates analysis, data pre-processing, and
package infrastructure. Illustrations are provided in Section
\ref{sec:casestudies} for a range of supervised learning tasks with
categorical and quantitative response variables. These show how the
local explanations can be used to get an overview of the model's use of
predictors, and to investigate errors in the model predictions. Section
\ref{sec:cheemdiscussion} concludes with a summary of the insights
gained. The methods are implemented in the \textbf{R} package
\textbf{cheem}.

@@

Local explanations shed light on nonlinear model fits by estimating
linear variable importance in the vicinity of a single observation.
There are many approaches for calculating local explanations. A
comprehensive summary of the taxonomy of currently available methods is
provided in Figure 6 by \citet{arrieta_explainable_2020}. It includes a
large number of model-specific explanations such as deepLIFT
\citep{shrikumar_not_2016, shrikumar_learning_2017}, a popular recursive
method for estimating importance in neural networks. There are fewer
model-agnostic methods, of which LIME, \citep{ribeiro_why_2016} SHaply
Additive exPlanations (SHAP), \citep{lundberg_unified_2017}, are
popular.

@@

We will be focusing on SHAP values in this this paper, but the approach
is applicable for any method used to calculate the local explanations.
SHAP calculates the variable contributions of one observation by
examining the effect of other variables on the predictions. The term
``SHAP'' refers to \citet{shapley_value_1953}'s method to evaluate an
individual's contribution in cooperative games by assessing this
player's performance in the presence or absence of other players.
\citet{strumbelj_efficient_2010} introduced SHAP for local explanations
in machine learning models. Variable importance can depend on the
sequence in which variables are entered into the model fitting process,
thus for any sequence we get a set of variable contribution values for a
single observation. These values will add up to the difference between
the fitted value for the observation, and the average fitted value for
all observations. Using all possible sequence, or permutation, gives
multiple values for each variable, which are averaged to get the SHAP
value for an observation. It can be helpful to standardize variables
prior to computing SHAP values, if they have been measured on different
scales.

The approach is related to partial dependence plots (see for example
\citet{molnar_interpretable_2020}), used to explain the effect of a
variable by predicting the response for a range of values on this
variable after fixing the value of all other variables to their mean.
Though partial dependence plots are a global approximation of the
variable importance, while SHAP is specific to one observation.

@@

@@

To explore the local explanations, coordinated views
\citep{roberts_state_2007} \citep[also known as ensemble
graphics,][]{unwin_ensemble_2018} are provided in the \emph{cheem
viewer} application. There are two primary plots: the \textbf{global
view} to give the context of all of the SHAP values and the
\textbf{radial tour view} to explore the local explanations with
user-controlled rotation. There are numerous user inputs, including
variable selection for the radial tour and observation selection for
making comparisons. There are different plots used for the categorical
and quantitative responses. Figures \ref{fig:classificationcase} and
\ref{fig:regressioncase} are screenshots showing the cheem viewer for
the two primary tasks: classification (categorical response) and
regression (quantitative response).

@@

The local explanations for all observations are normalized (sum of
squares equals 1), and thus, the relative importance of variables can be
compared across all observations. These are depicted as a vertical
parallel coordinate plot \citep{ocagne_coordonnees_1885}. (The SHAP
values of the PI and CI are shown as dashed and dotted lines,
respectively.) One should obtain a sense of the overall importance of
variables from this plot. The more important variables will have larger
values, and in the case of classification tasks variables which have
different magnitude for different classes are more globally important.
For example, Figure \ref{fig:classificationcase}e suggests that
\texttt{bl} is important for distinguishing the green class from the
other two. For regression, one might generally observe which variables
have low values for all observations (not important). For example,
\texttt{BMI} and \texttt{pwr} in Figure \ref{fig:regressioncase}e, have
a range of high and low values (e.g., \texttt{off}, \texttt{def}),
suggesting they are important for some observations and not important
for others.

@@

The time to preprocess the data will vary significantly with the
complexity of the model and local explanation. For reference, the FIFA
data contained 5000 observations of nine explanatory variables took 2.5
seconds to fit a random forest model of modest hyperparameters.
Extracting the tree SHAP values of each observation took 270 seconds
total. PCA and statistics of the variables and attributions took 2.8
seconds. These run times were from a non-parallelized session on a
modern laptop, but suffice to say that most of the time will be spent on
the local attribution. An increase in model complexity or data
dimensionality will quickly become an obstacle. Its reduced
computational complexity makes tree SHAP an excellent candidate to
start. Alternatively, the package \textbf{fastshap} claims extremely low
run times, attributed to fewer calls to the prediction function, partial
implementation in C++, and efficient use of logical subsetting,
\citet{greenwell_fastshap_2020}.

@@

\caption[Examining the local explanation for a PI which is dark (orange) chocolate incorrectly predicted to be milk (green)]{Examining the local explanation for a PI which is dark (orange) chocolate incorrectly predicted to be milk (green). From the attribution projection, this chocolate correctly looks more like dark than milk, which suggests that the local explanation does not help understand the prediction for this observation. So, the contribution of Sugar is varied---reducing it corresponds primarily with an increased magnitude from Fiber. When Sugar is zero, Fiber contributes strongly towards the left. In this view, the PI is closer to the bulk of the milk chocolates, suggesting that the prediction put a lot of importance on Fiber. This chocolate is a rare dark chocolate without any Fiber leading to it being mistaken for a milk chocolate. (A video of the tour animation can be found at https://vimeo.com/666431143.)}\label{fig:casechocolates}
\end{figure}
\end{CodeChunk}

@@

\caption[Examining the local explanation for a PI which is milk (green) chocolate incorrectly predicted to be dark (orange)]{Examining the local explanation for a PI which is milk (green) chocolate incorrectly predicted to be dark (orange). In the attribution projection, the PI could be either milk or dark. Sodium and Fiber have the largest differences in attributed variable importance, with low values relative to other milk chocolates. The lack of importance attributed to these variables is suspected of contributing to the mistake, so the contribution of Sodium is varied. If Sodium had a larger contribution to the prediction (like in this view). the PI would look more like other milk chocolates. (A video of the tour animation can be found at https://vimeo.com/666431148.)}\label{fig:casechocolatesinverse}
\end{figure}
\end{CodeChunk}

@@

\caption[Exploring the wages relative to skill measurements in the FIFA 2020 data]{Exploring the wages relative to skill measurements in the FIFA 2020 data. Star offensive player (L. Messi) is the PI, and he is compared with a top defensive player (V. van Dijk). The attribution projection is shown on the left, and it can be seen that this combination of variables produces a view where Messi has very high predicted (and observed) wages. Defense (`def`) is the chosen variable to vary. It starts very low, and Messi's predicted wages decrease dramatically as its contribution increases (right plot). The increased contribution in defense comes at the expense of offensive and reaction skills. The interpretation is that Messi's high wages are most attributable to his offensive and reaction skills, as initially provided by the local explanation. (A video of the animated radial tour can be found at https://vimeo.com/666431163.)}\label{fig:casefifa}
\end{figure}
\end{CodeChunk}

Figure \ref{fig:casefifa} tests the support of the local explanation.
Offensive and reaction skills (\texttt{off} and \texttt{rct}) are both
crucial to explaining a star offensive player. If either of them were
rotated out, the other would be rotated into the frame, maintaining a
far-right position. However, increasing the contribution of a variable
with low importance would rotate both variables out of the frame.

@@

\caption[Exploring an observation with an extreme residual as the PI in relation to an observation with an accurate prediction for a similarly priced house in a random forest fit to the Ames housing data]{Exploring an observation with an extreme residual as the PI in relation to an observation with an accurate prediction for a similarly priced house in a random forest fit to the Ames housing data. The local explanation indicates a sizable attribution to Lot Area (`LtA`), while the CI has minimal attribution to this variable. The PI has a higher predicted value than the CI in the attribution projection. Reducing the contribution of Lot Area brings these two prices in line. This suggests that if the model did not value Lot Area so highly for this observation, then the observed sales price would be quite similar. That is, the large residual is due to a lack of factoring in the Lot Area for the prediction of PI's sales price. (A video showing the animation is at https://vimeo.com/666431134.)}\label{fig:caseames}
\end{figure}
\end{CodeChunk}

@@

There is a clear need to extend the interpretability of black box
models. With techniques such as SHAP, LIME, Break-down, one can
calculate local explanations, i.e.~for every observation in the data.
These techniques quantify for each observation how strongly particular
variables affect the model's predictions. Surprisingly few techniques
allow us to understand the global distribution of these local
explanations. Unsupervised data exploration techniques applied to data
show how useful they are for identifying outliers, identifying segments
of observations or discovering correlations between variables. All of
these tasks can be performed for a set of explanations.

To address this challenge in this paper provides a technique that builds
on local explanations to explore the variable importance local to an
observation. The local explanations of an attribution projection from
which variable contributions are varied using a radial tour. Several
diagnostic plots are provided to assist with understanding the
sensitivity of the prediction to particular variables. A global view
shows the data space, explanation space, and residual plot. The user can
interactively select observations to compare, contrast, and study
further. Then the radial tour is used to explore the variable
sensitivity identified by the attribution projection.

This approach has been illustrated using four data examples of random
forest models with the tree SHAP local explanation. Local explanations
focus on the model fit, and help to dissect which variables are most
responsible for the fitted value. They can also form the basis of
learning how the model has got it wrong, with when the observation is
misclassified or has a large residual.

@@

An implementation is provided in the open-source \textbf{R} package
\textbf{cheem}, available on CRAN at
\url{https://CRAN.R-project.org/package=cheem}. Example data sets are
provided, and you can upload your data after model fitting and computing
the local explanations. The local explanations need to be pre-computed
and uploaded. Examples show how to do this for tree SHAP values, using
\textbf{treeshap} (tree based models from \textbf{gbm},
\textbf{lightgbm}, \textbf{randomForest}, \textbf{ranger}, or
\textbf{xgboost} \citet{greenwell_gbm_2020}; \citet{shi_lightgbm_2022};
\citet{liaw_classification_2002}; \citet{wright_ranger_2017};
\citet{chen_xgboost_2021}, respectively). The SHAP and oscillation
explanations could be easily added using \texttt{DALEX::explain()}
\citep{biecek_dalex_2018, biecek_explanatory_2021}.

The application was made with \textbf{shiny} \citep{chang_shiny_2021}.
The tour visual is built with \textbf{spinifex}
\citep{spyrison_spinifex_2020}. Both views are created first with
\textbf{ggplot2} \citep{wickham_ggplot2_2016} and then rendered as
interactive \texttt{html} widgets with \textbf{plotly}
\citep{sievert_interactive_2020}. \textbf{DALEX}
\citep{biecek_dalex_2018} and the free ebook, \emph{Explanatory Model
Analysis} \citep{biecek_explanatory_2021} were a boon to understanding
local explanations and how to apply them.

@@

Follow the examples provided with the package to compute the local
explanation (using \texttt{?cheem\_ls}). The application expects the
output returned by \texttt{cheem\_ls()}, saved to an \texttt{rds} file
with \texttt{saveRDS()} to be uploaded.

>>>>

Explainable Artificial Intelligence (XAI) is an emerging field of
research focused on methods for the interpreting of models
\citep{adadi_peeking_2018, arrieta_explainable_2020}. A class of
techniques, called \emph{local explanations} (LEs), provide methods to
approximate linear variable importance, called local variable
attributions (LVAs), at the location of each observation or the
predictions at a specific point in the data domain. Because these are
point-specific, it is challenging to comprehensively visualize them to
understand a model. There are common approaches for visualizing
high-dimensional data as a whole, but what is needed are new approaches
for viewing these individual LVAs relative to the whole.

For multivariate data visualization, a \emph{tour}
\citep{asimov_grand_1985, buja_grand_1986, lee_state_2021} of linear
data projections onto a lower-dimensional space, could be an element of
XAI, complementing LVAs. Applying tours to model interpretation is
recommended in \citet{wickham_visualizing_2015} primarily to examine the
fitted model in the space of the data. \citet{cook_interactive_2007}
describe the use of tours for exploring classification boundaries and
model diagnostics
\citep{Caragea2008, lee_pptree_2013, da_silva_projection_2021}. There
are various types of tours. In a \emph{manual} or radial tour
\citep{cook_manual_1997, spyrison_spinifex_2020}, the path of linear
projections is defined by changing the contribution of a selected
variable. We propose to use this to scrutinize the LVAs. This approach
could be considered to be a counter-factual, what-if analysis, such as
\emph{ceteris paribus} (``other things held constant'') profiles
\citep{biecek_ceterisparibus_2020}.

The remainder of this paper is organized as follows. Section
\ref{sec:explanations} covers the background of the LEs and the
traditional visuals produced. Section \ref{sec:tour} explains the tours
and particularly the radial manual tour. Section \ref{sec:cheemviewer}
discusses the visual layout in the graphical user interface and how it
facilitates analysis, data pre-processing, and package infrastructure.
Illustrations are provided in Section \ref{sec:casestudies} for a range
of supervised learning tasks with categorical and quantitative response
variables. These show how the LVAs can be used to get an overview of the
model's use of predictors, and to investigate errors in the model
predictions. Section \ref{sec:cheemdiscussion} concludes with a summary
of the insights gained. The methods are implemented in the \textbf{R}
package \textbf{cheem}.

@@

LVAs shed light on machine learning model fits by estimating linear
variable importance in the vicinity of a single observation. There are
many approaches for calculating LVAs. A comprehensive summary of the
taxonomy of currently available methods is provided in Figure 6 by
\citet{arrieta_explainable_2020}. It includes a large number of
model-specific explanations such as deepLIFT
\citep{shrikumar_not_2016, shrikumar_learning_2017}, a popular recursive
method for estimating importance in neural networks. There are fewer
model-agnostic methods, of which LIME \citep{ribeiro_why_2016} and
SHaply Additive exPlanations (SHAP) \citep{lundberg_unified_2017}, are
popular.

@@

We will be focusing on SHAP values in this this paper, but the approach
is applicable for any method used to calculate the LVAs. SHAP calculates
the variable contributions of one observation by examining the effect of
other variables on the predictions. The term ``SHAP'' refers to
\citet{shapley_value_1953}'s method to evaluate an individual's
contribution in cooperative games by assessing this player's performance
in the presence or absence of other players.
\citet{strumbelj_efficient_2010} introduced SHAP for LEs in machine
learning models. Variable importance can depend on the sequence in which
variables are entered into the model fitting process, thus for any
sequence we get a set of variable contribution values for a single
observation. These values will add up to the difference between the
fitted value for the observation, and the average fitted value for all
observations. Using all possible sequence, or permutation, gives
multiple values for each variable, which are averaged to get the SHAP
value for an observation. It can be helpful to standardize variables
prior to computing SHAP values, if they have been measured on different
scales.

The approach is related to partial dependence plots (see for example,
chapter 8 of \citet{molnar2022}), used to explain the effect of a
variable by predicting the response for a range of values on this
variable after fixing the value of all other variables to their mean.
Though partial dependence plots are a global approximation of the
variable importance, while SHAP is specific to one observation.

@@

There are numerous R packages currently available which provide
functions for computing SHAP values, including \texttt{fastshap}
\citep{fastshap}, \texttt{kernelshap} \citep{kernelshap}, \texttt{shapr}
\citep{shapr}, \texttt{shapviz} \citep{shapviz}, \texttt{PPtreeregViz}
\citep{PPtreeregViz}, and the package \texttt{DALEX} has many resources
\citep{biecek_dalex_2018}. There are many more packages only available
through Github, like \texttt{treeshap}
{[}kominsarczyk\_treeshap\_2021{]} that is used for this work.
\citet{molnar2022} provides good explanations of the different methods
and how to apply them to different models.

@@

To explore the LVAs, coordinated views \citep{roberts_state_2007}
\citep[also known as ensemble graphics,][]{unwin_ensemble_2018} are
provided in the \emph{cheem viewer} application. There are two primary
plots: the \textbf{global view} to give the context of all of the SHAP
values and the \textbf{radial tour view} to explore the LVAs with
user-controlled rotation. There are numerous user inputs, including
variable selection for the radial tour and observation selection for
making comparisons. There are different plots used for the categorical
and quantitative responses. Figures \ref{fig:classificationcase} and
\ref{fig:regressioncase} are screenshots showing the cheem viewer for
the two primary tasks: classification (categorical response) and
regression (quantitative response).

@@

The LVAs for all observations are normalized (sum of squares equals 1),
and thus, the relative importance of variables can be compared across
all observations. These are depicted as a vertical parallel coordinate
plot \citep{ocagne_coordonnees_1885}. (The SHAP values of the PI and CI
are shown as dashed and dotted lines, respectively.) One should obtain a
sense of the overall importance of variables from this plot. The more
important variables will have larger values, and in the case of
classification tasks variables which have different magnitude for
different classes are more globally important. For example, Figure
\ref{fig:classificationcase}e suggests that \texttt{bl} is important for
distinguishing the green class from the other two. For regression, one
might generally observe which variables have low values for all
observations (not important). For example, \texttt{BMI} and \texttt{pwr}
in Figure \ref{fig:regressioncase}e, have a range of high and low values
(e.g., \texttt{off}, \texttt{def}), suggesting they are important for
some observations and not important for others.

@@

The time to preprocess the data will vary significantly with the
complexity of the model and the LE. For reference, the FIFA data
contained 5000 observations of nine explanatory variables took 2.5
seconds to fit a random forest model of modest hyperparameters.
Extracting the tree SHAP values of each observation took 270 seconds
total. PCA and statistics of the variables and attributions took 2.8
seconds. These run times were from a non-parallelized session on a
modern laptop, but suffice to say that most of the time will be spent on
the LVA. An increase in model complexity or data dimensionality will
quickly become an obstacle. Its reduced computational complexity makes
tree SHAP an excellent candidate to start. Alternatively, the package
\textbf{fastshap} claims extremely low run times, attributed to fewer
calls to the prediction function, partial implementation in C++, and
efficient use of logical subsetting, \citet{greenwell_fastshap_2020}.

@@

\caption[Examining the LVA for a PI which is dark (orange) chocolate incorrectly predicted to be milk (green)]{Examining the LVA for a PI which is dark (orange) chocolate incorrectly predicted to be milk (green). From the attribution projection, this chocolate correctly looks more like dark than milk, which suggests that the LVA does not help understand the prediction for this observation. So, the contribution of Sugar is varied---reducing it corresponds primarily with an increased magnitude from Fiber. When Sugar is zero, Fiber contributes strongly towards the left. In this view, the PI is closer to the bulk of the milk chocolates, suggesting that the prediction put a lot of importance on Fiber. This chocolate is a rare dark chocolate without any Fiber leading to it being mistaken for a milk chocolate. (A video of the tour animation can be found at https://vimeo.com/666431143.)}\label{fig:casechocolates}
\end{figure}
\end{CodeChunk}

@@

\caption[Examining the LVA for a PI which is milk (green) chocolate incorrectly predicted to be dark (orange)]{Examining the LVA for a PI which is milk (green) chocolate incorrectly predicted to be dark (orange). In the attribution projection, the PI could be either milk or dark. Sodium and Fiber have the largest differences in attributed variable importance, with low values relative to other milk chocolates. The lack of importance attributed to these variables is suspected of contributing to the mistake, so the contribution of Sodium is varied. If Sodium had a larger contribution to the prediction (like in this view). the PI would look more like other milk chocolates. (A video of the tour animation can be found at https://vimeo.com/666431148.)}\label{fig:casechocolatesinverse}
\end{figure}
\end{CodeChunk}

@@

\caption[Exploring the wages relative to skill measurements in the FIFA 2020 data]{Exploring the wages relative to skill measurements in the FIFA 2020 data. Star offensive player (L. Messi) is the PI, and he is compared with a top defensive player (V. van Dijk). The attribution projection is shown on the left, and it can be seen that this combination of variables produces a view where Messi has very high predicted (and observed) wages. Defense (`def`) is the chosen variable to vary. It starts very low, and Messi's predicted wages decrease dramatically as its contribution increases (right plot). The increased contribution in defense comes at the expense of offensive and reaction skills. The interpretation is that Messi's high wages are most attributable to his offensive and reaction skills, as initially provided by the LVA. (A video of the animated radial tour can be found at https://vimeo.com/666431163.)}\label{fig:casefifa}
\end{figure}
\end{CodeChunk}

Figure \ref{fig:casefifa} tests the support of the LVA. Offensive and
reaction skills (\texttt{off} and \texttt{rct}) are both crucial to
explaining a star offensive player. If either of them were rotated out,
the other would be rotated into the frame, maintaining a far-right
position. However, increasing the contribution of a variable with low
importance would rotate both variables out of the frame.

@@

\caption[Exploring an observation with an extreme residual as the PI in relation to an observation with an accurate prediction for a similarly priced house in a random forest fit to the Ames housing data]{Exploring an observation with an extreme residual as the PI in relation to an observation with an accurate prediction for a similarly priced house in a random forest fit to the Ames housing data. The LVA indicates a sizable attribution to Lot Area (`LtA`), while the CI has minimal attribution to this variable. The PI has a higher predicted value than the CI in the attribution projection. Reducing the contribution of Lot Area brings these two prices in line. This suggests that if the model did not value Lot Area so highly for this observation, then the observed sales price would be quite similar. That is, the large residual is due to a lack of factoring in the Lot Area for the prediction of PI's sales price. (A video showing the animation is at https://vimeo.com/666431134.)}\label{fig:caseames}
\end{figure}
\end{CodeChunk}

@@

There is a clear need to extend the interpretability of black box
models. With techniques such as SHAP, LIME, Break-down, one can
calculate LEs, i.e.~for every observation in the data. These techniques
quantify for each observation how strongly particular variables affect
the model's predictions. Surprisingly few techniques allow us to
understand the global distribution of these LEs. Unsupervised data
exploration techniques applied to data show how useful they are for
identifying outliers, identifying clusters of observations or
discovering correlations between variables. All of these tasks can be
performed for a set of explanations.

To address this challenge in this paper provides a technique that builds
on LEs to explore the variable importance local to an observation. The
LVA is converted into an attribution projection from which variable
contributions are varied using a radial tour. Several diagnostic plots
are provided to assist with understanding the sensitivity of the
prediction to particular variables. A global view shows the data space,
explanation space, and residual plot. The user can interactively select
observations to compare, contrast, and study further. Then the radial
tour is used to explore the variable sensitivity identified by the
attribution projection.

This approach has been illustrated using four data examples of random
forest models with the tree SHAP LVA. LEs focus on the model fit, and
help to dissect which variables are most responsible for the fitted
value. They can also form the basis of learning how the model has got it
wrong, with when the observation is misclassified or has a large
residual.

@@

An implementation is provided in the open-source \textbf{R} package
\textbf{cheem}, available on CRAN at
\url{https://CRAN.R-project.org/package=cheem}. Example data sets are
provided, and you can upload your data after model fitting and computing
the LVAs. The LVAs need to be pre-computed and uploaded. Examples show
how to do this for tree SHAP values, using \textbf{treeshap} (tree based
models from \textbf{gbm}, \textbf{lightgbm}, \textbf{randomForest},
\textbf{ranger}, or \textbf{xgboost} \citet{greenwell_gbm_2020};
\citet{shi_lightgbm_2022}; \citet{liaw_classification_2002};
\citet{wright_ranger_2017}; \citet{chen_xgboost_2021}, respectively).
The SHAP and oscillation explanations could be easily added using
\texttt{DALEX::explain()}
\citep{biecek_dalex_2018, biecek_explanatory_2021}.

The application was made with \textbf{shiny} \citep{chang_shiny_2021}.
The tour visual is built with \textbf{spinifex}
\citep{spyrison_spinifex_2020}. Both views are created first with
\textbf{ggplot2} \citep{wickham_ggplot2_2016} and then rendered as
interactive \texttt{html} widgets with \textbf{plotly}
\citep{sievert_interactive_2020}. \textbf{DALEX}
\citep{biecek_dalex_2018} and \emph{Explanatory Model Analysis}
\citep{biecek_explanatory_2021} are helpfule for understanding LEs and
how to apply them.

@@

Follow the examples provided with the package to compute the LVAs (using
\texttt{?cheem\_ls}). The application expects the output returned by
\texttt{cheem\_ls()}, saved to an \texttt{rds} file with
\texttt{saveRDS()} to be uploaded.
